A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor interactions with proteins and DNA

### 2024-08-12 index.qmd
add orcid id

---
title: "A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor interactions with proteins and DNA"
subtitle: "Analysis code for figures"
date: today
author:
  - name: Merle Skribbe
    orcid: 0009-0004-4486-2654
    email: merle.skribbe@gmail.com
    affiliations:
      - ref: fmi
      - ref: unibas
  - name: Charlotte Soneson
    orcid: 0000-0003-3833-2169
    email: charlotte.soneson@fmi.ch
    affiliations:
      - ref: fmi
      - ref: sib
  - name: Michael B Stadler
    orcid: 0000-0002-2269-4934
    email: michael.stadler@fmi.ch
    affiliations:
      - ref: fmi
      - ref: unibas
      - ref: sib
  - name: Michaela Schwaiger
    orcid: 0000-0002-4522-7810
    affiliations:
      - ref: fmi
      - ref: sib
  - name: Vishnu Narayanan Suma Sreechakram
    orcid: 0000-0002-7341-3354
    affiliations:
      - ref: giessen
  - name: Vytautas Iesmantavicius
    orcid: 0000-0002-2512-9957
    affiliations:
      - ref: fmi
  - name: Daniel Hess
    orcid: 0000-0002-1642-5404
    affiliations:
      - ref: fmi
  - name: Eliza Pandini Figueiredo Moreno
    affiliations:
      - ref: fmi
  - name: Sigurd Braun
    orcid: 0000-0001-6399-8574
    affiliations:
      - ref: giessen
  - name: Jan Seebacher
    orcid: 0000-0002-7858-2720
    affiliations:
      - ref: fmi
  - name: Sebastien Smallwood
    orcid: 0009-0006-8466-2459
    affiliations:
      - ref: fmi
  - name: Marc Bühler
    orcid: 0000-0001-6661-9795
    email: marc.buehler@fmi.ch
    affiliations:
      - ref: fmi
      - ref: unibas
affiliations:
  - id: fmi
    name: Friedrich Miescher Institute for Biomedical Research
    address: Fabrikstrasse 24
    postal-code: 4056
    city: Basel
    country: Switzerland
  - id: unibas
    name: University of Basel
    address: Petersplatz 10
    postal-code: 4003
    city: Basel
    country: Switzerland
  - id: sib
    name: SIB Swiss Institute of Bioinformatics
    address: Fabrikstrasse 24
    postal-code: 4056
    city: Basel
    country: Switzerland
  - id: giessen
    name: Institute for Genetics, Justus-Liebig-University Giessen
    city: Giessen
    country: Germany
license: MIT License
format: 
    html:
        embed-resources: true
        fig-cap-location: top
---

>>>>

---
title: "A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor interactions with proteins and DNA"
subtitle: "Analysis code for figures"
date: today
author:
  - name: Merle Skribbe
    orcid: 0009-0004-4486-2654
    email: merle.skribbe@gmail.com
    affiliations:
      - ref: fmi
      - ref: unibas
  - name: Charlotte Soneson
    orcid: 0000-0003-3833-2169
    email: charlotte.soneson@fmi.ch
    affiliations:
      - ref: fmi
      - ref: sib
  - name: Michael B Stadler
    orcid: 0000-0002-2269-4934
    email: michael.stadler@fmi.ch
    affiliations:
      - ref: fmi
      - ref: unibas
      - ref: sib
  - name: Michaela Schwaiger
    orcid: 0000-0002-4522-7810
    affiliations:
      - ref: fmi
      - ref: sib
  - name: Vishnu Narayanan Suma Sreechakram
    orcid: 0000-0002-7341-3354
    affiliations:
      - ref: giessen
  - name: Vytautas Iesmantavicius
    orcid: 0000-0002-2512-9957
    affiliations:
      - ref: fmi
  - name: Daniel Hess
    orcid: 0000-0002-1642-5404
    affiliations:
      - ref: fmi
  - name: Eliza Pandini Figueiredo Moreno
    orcid: 0009-0001-8483-4437
    affiliations:
      - ref: fmi
  - name: Sigurd Braun
    orcid: 0000-0001-6399-8574
    affiliations:
      - ref: giessen
  - name: Jan Seebacher
    orcid: 0000-0002-7858-2720
    affiliations:
      - ref: fmi
  - name: Sebastien Smallwood
    orcid: 0009-0006-8466-2459
    affiliations:
      - ref: fmi
  - name: Marc Bühler
    orcid: 0000-0001-6661-9795
    email: marc.buehler@fmi.ch
    affiliations:
      - ref: fmi
      - ref: unibas
affiliations:
  - id: fmi
    name: Friedrich Miescher Institute for Biomedical Research
    address: Fabrikstrasse 24
    postal-code: 4056
    city: Basel
    country: Switzerland
  - id: unibas
    name: University of Basel
    address: Petersplatz 10
    postal-code: 4003
    city: Basel
    country: Switzerland
  - id: sib
    name: SIB Swiss Institute of Bioinformatics
    address: Fabrikstrasse 24
    postal-code: 4056
    city: Basel
    country: Switzerland
  - id: giessen
    name: Institute for Genetics, Justus-Liebig-University Giessen
    city: Giessen
    country: Germany
license: MIT License
format: 
    html:
        embed-resources: true
        fig-cap-location: top
---
